Refinement for open automata

### 2021-05-10 2021-Refinement/report.tex

This new substitution can replace the standard substitution in the case where only one hole is filled and also in the parallel case.
In the parallel case the condition is checked after the parallel substitution because there is no guarantee that any order of sequential composition is non-locking for every substitution even if the parallel substitution is non-locking.
\begin{exi} % TODO
\begin{figure}
\centering
\input{}
\vrule
\input{}
\vrule
\input{}
\caption{}
\label{fig:pnls}
\end{figure}
An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO
\end{exi}
From this point and in the previous definitions, composition will only refer to non-locking composition.

>>>>

This new substitution can replace the standard substitution in the case where only one hole is filled and also in the parallel case.
In the parallel case the condition is checked after the parallel substitution because there is no guarantee that any order of sequential composition is non-locking for every substitution even if the parallel substitution is non-locking.
%\begin{exi} % TODO
%\begin{figure}
%\centering
%\input{}
%\vrule
%\input{}
%\vrule
%\input{}
%\caption{}
%\label{fig:pnls}
%\end{figure}
An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO HERE
%\end{exi}
From this point and in the previous definitions, composition will only refer to non-locking composition.
